A Reduced Representation for Computational Fabrication

### 2013-05-03 thesis/1_cover.tex
add cover page

\vspace{.1in}
Donglai Wei \\

@@

\noindent
Certified by: \underline{\mbox{\hspace{4.827in}}} \\
\vspace{-.25in}
{\flushright Your first supervisor's name here \\
Title of supervisor, e.g., Professor of Electrical Engineering and Computer Science \\
Thesis Supervisor \\
}

>>>>

\vspace{.1in}
Desai Chen\\

@@

\noindent
Certified by: \underline{\mbox{\hspace{4.827in}}} \\
\vspace{-.25in}
{\flushright Wojciech Matusik\\
Title of supervisor, Associate Professor of Electrical Engineering and Computer Science \\
Thesis Supervisor \\
}
